Combinatorics of the geometry of Wilson loop diagrams

### 2019-02-07 General WLD combinatorics.tex
Inside/outside dfn version 2.2

Note that for any Wilson loop diagram, $W = (\cP, n)$, each propagator $p$ partions $[n]$ into two cyclic subintervals of $[n]$, $\{[i+1, j], [j+1, i]\}$ that lie on either side of $p$. In the sequel we refer to these intervals as an interval inside and outside of $p$, depending on a ordering we associate to the propagator.

>>>>

Note that for any Wilson loop diagram, $W = (\cP, n)$, each propagator $p$ partions $[n]$ into three subsets of $[n]$, $\{[i+2, j-1], V(p), [j+2, i-1]\}$, the support of $p$ and the vertices that lie on either side of $p$. In the sequel we refer to the latter two intervals as an interval inside and outside of $p$, depending on a ordering we associate to the propagator.
